Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL

### 2015-04-17 Paper2015.tex
Modified text on neutron results

\subsection{Neutron fluence rate, spatial distribution and spectrum}
Fig.~\ref{fig:SUPDensity} shows neutron spatial distribution at the SUP, for neutrons above \SI{10}{\MeV}.
The collimation effect is clearly visible.
Within the beam umbra the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt13} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from the standard facility parameterisation~\cite{Prokofiev2009}.
The parameterisation therefore exceeds the present calculations by 31\%.

@@

Fig.~\ref{fig:Lethargyplots}

@@

Fig.~\ref{fig:SUPSpectraComparison} compares calculated neutron yield versus energy in the umbra at the SUP with that predicted by the naked-target simulation~\cite{Platt13} and with the standard ANITA SUP parameterisation~\cite{Prokofiev2009}.
The results show\ldots
\todo{Discuss the results. Compare current with earlier calculations. Compare calculations with parameterisation.}

Fig.~\ref{fig:CUPSpectraComparison} compares the spectrum calculated at the CUP with that from the standard parameterisation~\cite{Prokofiev14}.
The latter curve is derived from MCNPX calculations supported by TOF measurements with TFBCs.
The results show\ldots
\todo{Explain what the results show: CUP measurement comparison.}

@@

\subsection{Neutron time of flight}
Neutron beam monitoring and characterisation at TSL uses time-of flight measurements with \U238\ TFBCs.
Our Geant4 model permits these measurements to be simulated.
Neutron time of flight data from the simulation (time measured from the time of arrival of primary photons at the target to the time of arrival of secondary neutrons at the point of interest) were folded in energy with the \U238\ fission cross-section, convolved with a \SI{5}{\ns} rectangle function approximating the primary proton micropulse shape, and overlapped at \SI{45}{\ns}, representing the timing ambiguity due to the micropulse period.
Results are presented here for the CUP-TOF position and compared with measurements~\cite{Prokofiev14} in Fig.~\ref{fig:TOFSpectra}.
The simulated CUP-TOF results were calculated for the \SI{3}{\cm} collimator, to match the available measured data.
The results show\ldots
\todo{Explain what the results show.}

@@

\subsection{Gamma fluence rate, spatial distribution and dose rate}
Fig.~\ref{fig:GammaSpatialDistribution} shows the calculated spatial distribution of gamma photons at SUP and CUP.
Fig.~\ref{fig:DifferentialGammaSpectra} shows the calculated differential gamma spectra within the central region of the spatial distribution.
The results show\ldots
\todo{Describe the gamma results}

>>>>

\subsection{Neutrons}
Fig.~\ref{fig:SUPDensity} shows neutron spatial distribution at the SUP, for neutrons above \SI{10}{\MeV}.
The collimation effect is clearly visible.
Within the beam umbra the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt13} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from the standard facility parameterisation~\cite{Prokofiev2009}.
The parameterisation therefore exceeds the present calculations by 31\%.

@@

Fig.~\ref{fig:Lethargyplots} compares calculates spectra at SUP and CUP with their respective standard facility models~\cite{Prokofiev2009,Prokofiev14}.
The SUP data are also compared with results from preliminary Geant4 simulations~\cite{Platt13}.
The results show\ldots
\todo{Describe the neutron spectra.}

@@

@@

Neutron beam monitoring and characterisation at TSL includes time-of flight measurements with \U238\ TFBCs~\cite{Prokofiev14}.
Fig.~\ref{fig:TOFSpectra} compares simulated and measured TOF spectra at the CUP-TOF position.
The simulated CUP-TOF results were calculated for the \SI{3}{\cm} collimator, to match the measured data.
Neutron time of flight data from the simulation were folded in energy with the \U238\ fission cross-section, convolved with a \SI{5}{\ns} rectangle function approximating the primary proton micropulse shape, and overlapped at \SI{45}{\ns}, representing the timing ambiguity due to the micropulse period.
The results show\ldots
\todo{Explain what the results show.}

@@

\subsection{Photons}
Fig.~\ref{fig:GammaSpatialDistribution} shows the calculated spatial distribution of gamma photons at SUP and CUP.
Fig.~\ref{fig:DifferentialGammaSpectra} shows the calculated differential gamma spectra within the central region of the spatial distribution.
The results show\ldots
\todo{Describe the gamma results}
